### 2010-03-23 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: justify introduction of \DProd

In the alternative presentation, we go further and present all our
codes as quotations of standard type-formers. This presentation is
shown in Figure~\ref{fig:type-former-desc}.
\note{pwm: The exception being non dependent product -- we might want to
explain why this is.}

>>>>

In the alternative presentation, we go further and present all our
codes as quotations of standard type-formers. This presentation is
shown in Figure~\ref{fig:type-former-desc}. The reader will notice the
introduction of $\DProd{}{}$ that overlaps with $\DSigma{}{}$. Unlike
$\DSigma{}{}$, $\DProd{}{}$ is first-order, hence amenable to a
definitional treatment. \note{We could replace $\DUnit$ by $\DConst$
  here, instead of doing it in the following section. This is also a
  story about being first-order, so that would make sense, isn't it?}
